Data Management \\ and LSST Special Programs

### 2018-06-18 DMTN-065.tex
fixed typo

{\bf The LSST Project's Role in Processing Special Programs Data -- } The LSST Project will not take formal responsibility for specialized data reduction algorithms needed to process data, including images taken in non-standard modes. The term "specialized algorithms" refers to software that is not already within scope of the LSST Data Management (DM) science pipelines, and may include, for example: difference imaging for short exposures in which the PSF is not well-formed, shift-and-stack for faint moving objects, or any software with computational needs that significantly surpass the processing budget per image (compared to the processing of a WFD image). The Project will incorporate Special Programs data into the Prompt and/or Data Release processing pipelines and data products of the WFD Main Survey, such as {\tt Alerts}, {\tt CoAdds}, or {\tt Source} and {\tt Object} catalogs (with appropriate flags; LSST data products are described in \citeds{LSE-163}), whenever this (1) can be accomplished with existing software, and (2) is scientifically beneficial to that data product. The Project will also reconfigure its pipelines to generate separate imaging and catalog data products for Special Programs, whenever this can be accomplished with existing software. Finally, the Project will enable user-generated processing via the Science Platform (\citeds{LSE-319}), which will provide software tools and computational resources for (re)processing LSST data.

@@

{\bf Filter Changes -- } The maximum time for filter change is $120$ seconds: $30$ seconds for the telescope to reorient the camera to its nominal zero angle position on the rotator, and $90$ seconds to the camera subsystem for executing the change (OSS-REQ-0293; \citeds{LSE-30}). Assuming that most Special Programs would be designed to keep overheads $<100\%$ and would be using standard $30$ second visits, the filter change time indicates that it is likely that at least $4 exposures$ in a given filter would be obtained between filter changes -- but this is not actually a technical boundary.

>>>>

{\bf The LSST Project's Role in Processing Special Programs Data -- } The formal requirements regarding LSST's role in processing Special Programs data are in \citeds{LSE-61}, and the following statements have been derived from those requirements. The LSST Project will not take formal responsibility for specialized data reduction algorithms needed to process data, including images taken in non-standard modes. The term "specialized algorithms" refers to software that is not already within scope of the LSST Data Management (DM) science pipelines, and may include, for example: difference imaging for short exposures in which the PSF is not well-formed, shift-and-stack for faint moving objects, or any software with computational needs that significantly surpass the processing budget per image (compared to the processing of a WFD image). The Project will incorporate Special Programs data into the Prompt and/or Data Release processing pipelines and data products of the WFD Main Survey, such as {\tt Alerts}, {\tt CoAdds}, or {\tt Source} and {\tt Object} catalogs (with appropriate flags; LSST data products are described in \citeds{LSE-163}), whenever this (1) can be accomplished with existing software, and (2) is scientifically beneficial to that data product. The Project will also reconfigure its pipelines to generate separate imaging and catalog data products for Special Programs, whenever this can be accomplished with existing software. Finally, the Project will enable user-generated processing via the Science Platform (\citeds{LSE-319}), which will provide software tools and computational resources for (re)processing LSST data.

@@

{\bf Filter Changes -- } The maximum time for filter change is $120$ seconds: $30$ seconds for the telescope to reorient the camera to its nominal zero angle position on the rotator, and $90$ seconds to the camera subsystem for executing the change (OSS-REQ-0293; \citeds{LSE-30}). Assuming that most Special Programs would be designed to keep overheads $<100\%$ and would be using standard $30$ second visits, the filter change time indicates that it is likely that at least $4$ exposures in a given filter would be obtained between filter changes -- but this is not actually a technical boundary.
